---
title: "Data Visualization"
author: "Zeid El Ameli"
date: "5/1/2022"
output: html_document
fig_width: 20
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Libraries
library(ggplot2)
library(tidyverse)
library(hrbrthemes)
library(rpivotTable)
# Load dataset (csv)
data <- read.csv("C:/Users/zeida/Documents/superstore.csv", header=TRUE)

# plot
counts <- table(data$State)
barplot(counts, main="Oders by State",xlab="State", ylab="Number of Orders", las=2)

```

## Barplots
Bar plots are a great way to quickly scan your data, it gives us a brief overview of what we're dealing with.
Below is an example of the number of orders by state for a large superstore.

```{r barplot, fig.height=7, fig.width=14}
# Load dataset (csv)
data <- read.csv("C:/Users/zeida/Documents/superstore.csv", header=TRUE)


# plot
counts <- table(data$State)
barplot(counts, main="Oders by State", ylab="Number of Orders", las=2)

```

## Other Iterations of plots

You can slice and dice your data however you please. To make your job easier, use pivoted charts for a powerful, interactive analytics experience!

Note that the default pivoted chart below is a bar chart of the sum of sales ($) by state, feel free to play with it however you want! 

- use the chart type selector on the top left to change the way you want to visualize your data
- use the aggregation function seelctor (how to group your data) to choose what metrics you're interested in.
- use the selector below the aggregator (where it says "Sales") to choose what do you want to aggregate
- use the blank space on top of the chart to add/remove groups of data (the default here is "State", but you can drag it out and/or add another type of grouping) 

```{r pivot, echo=FALSE}
rpivotTable(data, aggregatorName= "Sum", vals="Sales", cols="State", rendererName= "Bar Chart")
```
